### 2018-01-27 includes/problems.tex
Addressing Murphy's feedback.

    We generated several suites of string and regex problems using \fuzzer{}. These problems are available at \problemRepo{}. Below, we describe the \texttt{generated} suite that we generated using \generator{}: \\

>>>>

    We generated several suites of string and regex problems using \fuzzer{}. \footnote{For review anonymity, we removed the link to the problem repository. It will be provided separately in the artifact submission track and will appear in the final version of the paper.} Below, we describe the \texttt{generated} suite that we generated using \generator{}: \\

### 2018-01-27 includes/stringfuzz.tex
Addressing Murphy's feedback.

    This section describes the fuzzer \fuzzer{}, which generates new \smtfull{} problems and transforms existing ones. \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smtfull{} string problems.

    % Its source code repository is available at \sourceRepo{}. It can either be installed from source, or from the Python PIP package repository.

@@

        \fuzzer{} can generate and transform problems with regular expression constraints. The command \texttt{stringfuzzg regex} invokes the regex problem generator, and has several options to control its output. It generates a problem in the form\footnote{Variable declarations omitted for brevity.}:

>>>>

    This section describes the fuzzer \fuzzer{}, which generates new \smtfull{} problems and transforms existing ones. \fuzzer{} is implemented as a Python package, and comes with several executables to generate, transform, and analyse \smtfull{} string problems. It can either be installed from source, or from the Python PIP package repository. \footnote{For review anonymity, we removed the link to the source code. It will be provided separately in the artifact submission track and will appear in the final version of the paper.}

@@

        \fuzzer{} can generate and transform problems with regular expression constraints. The command \texttt{stringfuzzg regex} invokes the regex problem generator, and has several options to control its output. It generates a problem of the form\footnote{Variable declarations omitted for brevity.}:
